\section{Conclusions}\label{sec:conclusions}
In this paper, two main aspects of the calibration of KAPRI, a new polarimetric portable ground-based FMCW radar were discussed:
\begin{enumerate}
	\item The preprocessing of raw data into SLC images, taking into account several effects due to the specific hardware design of the system.
	\item The polarimetric calibration of data into phase and amplitude calibrated polarimetric covariance matrices.
\end{enumerate}
\subsection{Preprocessing}
 The particular antenna design causes a frequency-depending shift of the antenna mainlobe during the chirp that causes a worsened range resolution. It is corrected using a slow time-fast time interpolation procedure; significant range resolution improvement are observed after the correction.\\ The real aperture, azimuth scanning design results in a motion of the antenna phase center relative to the scatterers, causing an observable azimuth phase ramp in point target responses. The variation is significantly different between the antennas, with almost 30$^\circ$ over the 3 dB beamwidth for the V antenna and much smaller for the H unit. This additional phase will complicate polarimetric calibration if left unaltered; is corrected by a SAR-like azimuth filter that reduces the total phase variation to under 10$^\circ$.\\
Because separated transmitting and receiving antennas are used for each polarization, the polarimetric calibration is complicated by the presence of an interferometric baseline between channels that adds a topographic phase contribution in the polarimetric phase differences. Thanks to an additional interferometric baseline, the topographic contribution can be estimated and subtracted from each element of the covariance matrix affected by it.
\subsection{Calibration}
The resulting flattened covariance matrix is then calibrated  by assuming zero crosstalk and estimating copolar imbalances using a trihedral corner reflector assuming the parameters to be independent from the  incidence angle. The crosspolar imbalance is estimated using distributed targets under the assumption of reciprocity.\\
The calibration quality is assessed by estimating residual calibration parameter on a calibrated scene with five trihedral corner reflectors: the mean amplitude imbalance is close to unity while the mean residual phase imbalance is very close to zero, with an RMS of $7^\circ$; no significant variation with incidence angle is observed. These results suggest the suitability of the simplified calibration model for the calibration of fully polarimetric KAPRI data.
%The preprocessing starts with the correction of a frequency-depending shift of the antenna mainlobe direction, which reduces the range resolution of the data; this effect is caused by the slotted waveguide type antenna used by the system. The squint is corrected by a linear interpolation of the dechirped data in the chirp time-azimuth domain, yielding correctly focused range profiles resolved in azimuth by the antenna beamwidth.\\
%After the frequency dependent squint correction, an azimuthal phase ramp in the response of point-like scatterers was observed in the range compressed data, especially for the VV channel. A model was developed to explain this variation in terms of an antenna phase center horizontally displaced from the lever arm that causes a small variation in the slant range distance from the radar during the rotational scan. This change in range is too small compared to the range resolution to cause visible range cell migration. However, the variation in propagation path is suspected to induce the observed phase modulation. Using the model, the horizontal displacement was estimated and its effect was corrected using the model as a azimuth matched filter. The phase after the proposed filtering showed very little azimuthal variation and the data thus corrected can be used for polarimetric calibration.\\
%In the calibration procedure an additional step to remove the topographic phase contribution due to the spatial separation of the polarimetric phase centers was necessary. The topographic phase component was estimated with an interferogram obtained from channels with the same polarization separated by an nonzero baseline and rescaled to the equivalent baseline between the phase centers.\\ Once the topographic phase contribution was removed, the polarimetric calibration was performed by assuming zero crosstalk and estimating copolar imbalances using a trihedral corner reflector assuming the parameters to be independent from the  incidence angle. The crosspolar imbalances were estimated using distributed targets under the assumption of reciprocity.\\ The choice of neglecting crosstalk is supported by the use of temporal multiplexing for the acquisition of polarimetric data and by the high polarization purity of the antennas.\\ The calibration quality was tested by applying the method on a scene where five trihedral corner reflector were placed at different ranges from the radar. One of them was used to determine the parameters that where then applied to the entire image. Copolar phase and amplitude imbalances were then recomputed on the remaining reflectors; the mean amplitude imbalance is close to unity while the mean residual phase imbalance is very close to zero, with an RMS of $7^\circ$; no significant variation with incidence angle is observed. These results suggest the suitability of the simplified calibration model for the calibration of fully polarimetric KAPRI data.